Millions of Type Errors

### 2023-09-09 programming23/paper.tex
error density plots

%% Extra Roblox constraints:
%% - No access to some events: save, exit
%% - No idea if analysis widget is open, closed, or obscured
%% - Don't know which module is the data model
%%   (no ids for ANY module for that matter)

@@

@@

TODO .. somewhere ... out/error-density-*
TODO ... somewhere ... te leq fs : use error-density

@@

\begin{figure}[thb]
  %% TODO stacked bars?
  %% TODO align old;curr
  %% TODO sep'23 remove this??!
  \begin{tabular}{lrrrrr}
    Mode             & \# Rows & E         & Any Error & In Module & In range \\
      & & & & (old ; curr) &  (old ; curr) \\\midrule
    \mnocheck{}   &   4,471 & \code{te} &    5.77\% &  0.20\% ;  2.21\% &  0.16\% ;  0.63\% \\
                  &         & \code{fs} &   59.18\% & 32.81\% ; 49.16\% &  9.17\% ; 13.13\% \\
    \mnonstrict{} &     506 & \code{te} &   25.89\% & 12.06\% ; 18.18\% &  6.32\% ;  7.91\% \\
                  &         & \code{fs} &   62.45\% & 37.94\% ; 53.75\% & 16.60\% ; 20.75\% \\
    \mstrict{}    &      24 & \code{te} &   50.00\% & 29.17\% ; 33.33\% &     0\% ;     0\% \\
                  &         & \code{fs} &   62.50\% & 50.00\% ; 58.33\% &  4.17\% ;  8.33\% 
  \end{tabular}

  \caption{TODO}

\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=0.8\columnwidth]{img/example-error-delta.png}
  \caption{Errors delta, nonstrict}
  \label{f:error-delta}
\end{figure}

>>>>

Extra Roblox constraints:
- No access to some events: save, exit
- No idea if analysis widget is open, closed, or obscured
- Don't know which module is the data model
  (no ids for ANY module for that matter)

@@

    15 days

@@

@@

@@

% TODO .. somewhere ... out/error-density-*
%   row->te nocheck :: 48378 ++ , 9440 ==, 45479 --
%   row->te nonstrict :: 19491 ++ , 9567 ==, 20121 --
%   row->te strict :: 733 ++ , 368 ==, 770 --
% 
% TODO ... somewhere ... te leq fs : use error-density

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{img/error-count-nocheck-row->te-density-diff.pdf}
  \includegraphics[width=\columnwidth]{img/error-count-nonstrict-row->te-density-diff.pdf}
  \includegraphics[width=\columnwidth]{img/error-count-strict-row->te-density-diff.pdf}

  \begin{tabular}{lr@{}rr@{}rr@{}r}
    & \zerowidth{Add} & & \zerowidth{Keep} & & \zerowidth{Drop} \\\midrule
    \mnocheck{} & 48378 & [\pct{46.83}] & 9440 & [\pct{9.14}] & 45479 & [\pct{44.03}] \\
    \mnonstrict{} & 19491 & [\pct{39.63}] & 9567 & [\pct{19.45}] & 20121 & [\pct{40.91}] \\
    \mstrict{} & 733 & [\pct{39.18}] & 368 & [\pct{19.67}] & 770 & [\pct{41.15}] \\
  \end{tabular}
  \caption{FILL error density}
  \label{f:error-delta}
\end{figure}
